Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2015-01-20 paper/sheaf_lics.tex
some more typos

Another technical difficulty is the fact that sheafification in topos
theory uses the property that epimorphisms are coequalizers of their
kernel pairs. This properties does not hold anymore in higher toposes, but
using Giraud-Rezk-Lurie axioms of $\infty$-toposes, the same property
holds by replacing kernel pairs by \v{C}ech nerves in the statement.

Finally, one of the main difficulty in our formalization is that many
equalities which are trival (by proof irrelevance) in the topos-theoretic
setting becomes relevant and requires a carreful use of univalence
with appropriate isomorphisms and a lot of reasoning on equalities
between paths.

@@

The type of all modal $n$-types, \ie types for which $P$ holds, is
defined as %$\Type^\modal_p$, so 
$$
\Type_n^\modal \ \defeq \sum_{T : \Type_n} P (T).
$$
%
Since basic type formers (dependent products, products, sigma types)
preserves truncation levels, we can leverage all theorems on modalites
presented in~\cite[Chapter 7.7]{hottbook}.
%
We now summarize the main properties that are used in our
formalization. We do not recall the proofs as they are not specific to
our presentation (also the setting using truncated types provides
minor changes), but they can be found in our Coq formalization.

@@

%
If Coq handles cumulativity on $\Type$ natively, it is not
the case for the $\Sigma$-type $\Type_n$, which require propositional
resizing. 
%
This issue could be solved by adding an axiom of cumulativity
for $\Type_n$ with an explicit management of universes. 
%
But as it would not have any computational content, such a solution
would really complicate the proofs as the axiom would appear
everywhere cumulativity is needed and it would need explicitly
annotation for universe levels everywhere in the formalization.
%
We have chosen a more simple but maybe less satisfactory solution. 
%
When the absence of cumulativity on $\Type_n$ rises a universe issue
for a lemma (it occurs twice in the formalization), we have proved the
lemma and then admit the exact same lemma, just letting Coq infer less
constrained universe levels.

>>>>

Another technical difficulty is the fact that sheafification in topos
theory uses the property that epimorphisms are coequalizers of their
kernel pairs. This property does not hold anymore in higher toposes, but
using Giraud-Rezk-Lurie axioms of $\infty$-toposes, the same property
holds by replacing kernel pairs by \v{C}ech nerves in the statement.

Finally, one of the main difficulty in our formalization is that many
equalities which are trival (by proof irrelevance) in the topos-theoretic
setting become relevant and require a careful use of univalence
with appropriate isomorphisms and a lot of reasoning on equalities
between paths.

@@

The type of all modal $n$-types, \ie types for which $P$ holds, is
defined as %$\Type^\modal_p$, so 
$$
\Type_n^\modal \ \defeq \sum_{T : \Type_n} P (T).
$$
%
Since basic type formers (dependent products, products, sigma types)
preserve truncation levels, we can leverage all theorems on modalities
presented in~\cite[Chapter 7.7]{hottbook}.
%
We now summarize the main properties that are used in our
formalization. We do not recall the proofs as they are not specific to
our presentation (also the setting using truncated types provides
minor changes), but they can be found in our Coq formalization.

@@

%
If Coq handles cumulativity on $\Type$ natively, it is not
the case for the $\Sigma$-type $\Type_n$, which require propositional
resizing. 
%
This issue could be solved by adding an axiom of cumulativity
for $\Type_n$ with an explicit management of universes. 
%
But as it would not have any computational content, such a solution
would really complicate the proofs as the axiom would appear
everywhere cumulativity is needed and it would need explicit
annotations for universe levels everywhere in the formalization.
%
We have chosen a more simple but maybe less satisfactory solution. 
%
When the absence of cumulativity on $\Type_n$ rises a universe issue
for a lemma (it occurs twice in the formalization), we have proved the
lemma and then admit the exact same lemma, just letting Coq infer less
constrained universe levels.
